A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-12-09 kobakian-cook.Rmd
CRANpkg ref added

This paper contains a discussion of Existing Mapping Practices. This is followed by details of the Algorithm. The implementation section discusses the algorithm in the \pkg{sugarbag} package. Finally, the use and benefits of animation are presented.

@@

The algorithm is implemented in the \CRANpkg{sugarbag} package for `R`, named after the common name for the *Trigona carbonaria* bee – a species which builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH]. This unusual pattern also provided the inspiration for the algorithm, where the maps are constructed by building out from multiple focal points on the geographic map base in a spiral fashion.

@@

The results from various steps in the process are illustrated in Figure 5.

>>>>

This paper contains a discussion of Existing Mapping Practices. This is followed by details of the Algorithm. The implementation section discusses the algorithm in the \CRANpkg{sugarbag} package. Finally, the use and benefits of animation are presented.

@@

The algorithm is implemented in the \pkg{sugarbag} package for `R`, named after the common name for the *Trigona carbonaria* bee – a species which builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH]. This unusual pattern also provided the inspiration for the algorithm, where the maps are constructed by building out from multiple focal points on the geographic map base in a spiral fashion.

@@

The results from various steps in the process are illustrated in Figure \ref{fig:filterprocess}.
